---
title: "BS Ice Kohonen analysis - Multivariate (ICE and MSLP)"
output:
  html_notebook: default
  pdf_document: default
---

Using 8day averaged ice concentration data (S.Salo)
Choose a select group of locations on grid. (every 4th point)

```{r}
dp = read.csv('/Volumes/WDC_internal/Users/bell/in_and_outbox/2017/stabeno/Ice_kohonen/coords_subset_4pt_noland.asc2',header=TRUE,sep='')

```
Using NCEP Reanalysis II mean-daily 2m air temperature on four grid points (181.875,65.712 193.125,65.712 181.875,58.0939 193.125,58.0939)

Equivalent 8day averages are made (with the exception of the last chunk of the year.  Salo has 359-001, this is 359-365)

1979 DJ - 2017 DJ
Both files are on same time grid (which is the list of files from the DJ subset)
'coords_ncep_temp.asc2'

```{r}
library(kohonen)

ice_data = read.csv('/Volumes/WDC_internal/Users/bell/in_and_outbox/2017/stabeno/Ice_kohonen/1979-2016_4pt_noland_DF.asc')

temp_data = read.csv('/Volumes/WDC_internal/Users/bell/in_and_outbox/2017/stabeno/Ice_kohonen/1979-2017_NCEP_2mtemp.csv')
```
With variables read in, run multivariate SOM analysis.  Weight ice-75% and temp-25%
Do not scale any variables
```{r}
xyf.BS <- xyf(scale(temp_data,scale=FALSE,center=FALSE),scale(ice_data,scale=FALSE,center=FALSE),grid=somgrid(3,3,"hexagonal"),user.weights=c(0.25,0.75),maxNA.fraction=1,rlen=500)

summary(xyf.BS)

map(xyf.BS)
```

```{r}
getCodes(xyf.BS)
```
```{r}
plot(xyf.BS,"codes")

plot(xyf.BS,"quality")

plot(xyf.BS,"counts")

plot(xyf.BS,"changes")

plot(xyf.BS, type="dist.neighbours")
```